---
title: "Solutions to C4-C5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

# Chapter 4 Workflow: Basics

## Exercise 4

> 1.  Why does this code not work?
>
> ```{r, error = TRUE}
> my_variable <- 10
> my_varıable
> ```

调用数据的时候，把`i`写成了小写大写字母`ı`。

> 2.  Tweak each of the following R commands so that they run correctly:
>
> ```{r, eval = FALSE}
> libary(tidyverse)
> ggplot(dota = mpg) + 
>   geom_point(maping = aes(x = displ, y = hwy))
> ```

正确的应该是：

```{r 4.2, eval=FALSE}
library(tidyverse)
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
```

在输入的时候，部分借助自动补全，可以避免一些typos。

> 3.  Press Alt + Shift + K. What happens? How can you get to the same place using the menus?

输出快捷键表。Menu-Tools-Keyboard Shortcut Help。

# Chapter 5

## Exercise 5.2

> 1.  Find all flights that
>
> ```{=html}
> <!-- -->
> ```
> a.  Had an arrival delay of two or more hours
> b.  Flew to Houston (`IAH` or `HOU`)
> c.  Were operated by United, American, or Delta
> d.  Departed in summer (July, August, and September)
> e.  Arrived more than two hours late, but didn't leave late
> f.  Were delayed by at least an hour, but made up over 30 minutes in flight
> g.  Departed between midnight and 6am (inclusive)

```{r 5.2.1}
#a
filter(flights, arr_delay >= 120)
#b
filter(flights, dest %in% c('IAH','HOU'))
#c
filter(flights, carrier %in% c("AA", "DL", "UA"))
#d
filter(flights, month %in% 7:9)
#e
filter(flights, arr_delay > 120, dep_delay <= 0)
#f
filter(flights, dep_delay >= 60, dep_delay - arr_delay > 30)
#g
filter(flights, dep_time <= 600 | dep_time == 2400)
#filter(flights, dep_time %% 2400 <= 600)
```

> 2.  Another useful dplyr filtering helper is `between()`. What does it do? Can you use it to simplify the code needed to answer the previous challenges?

取某变量的范围[a,b]。 所以`filter(flights, month %in% 7:9)`也可以改为`filter(flights, between(month,7,9))`。

> 3.  How many flights have a missing `dep_time`? What other variables are missing? What might these rows represent?

`dep_time`缺失的样本，`arr_time`也缺失了，可能是取消的航班？

```{r 5.2.3}
# 首先可以筛选出NA的样本
filter(flights, is.na(dep_time))
# 要知道有多少个样本缺失值
summary(flights$dep_time)
# 或是
nrow(filter(flights, is.na(dep_time)))
```

> 4.  Why is `NA ^ 0` not missing? Why is `NA | TRUE` not missing? Why is `FALSE & NA` not missing? Can you figure out the general rule? (`NA * 0` is a tricky counterexample!)

任何数的零次方都等于1。\
"真或假"永远为真。\
"假和X"永远为假。\
基本上带有`NA`的运算都要注意`NaN`。

## Exercise 5.3

> 1.  How could you use `arrange()` to sort all missing values to the start? (Hint: use `is.na()`).

```{r 5.3.1}
arrange(flights, desc(is.na(dep_time)))
```

> 2.  Sort `flights` to find the flights with longest departure delays. Find the flights that left earliest.

```{r 5.3.2}
arrange(flights, desc(dep_delay))[1,]
arrange(flights, dep_delay)[1,]
```

> 3.  Sort `flights` to find the fastest (highest speed) flights. (Hint: try sorting by a calculation).

```{r 5.3.3}
arrange(flights, desc(distance / air_time))[1,]
```

> 4.  Which flights travelled the farthest? Which travelled the shortest?

```{r 5.3.4}
arrange(flights, desc(distance))[1,]
arrange(flights, distance)[1,]
```

## Exercise 5.4

> 1.  Brainstorm as many ways as possible to select `dep_time`, `dep_delay`, `arr_time`, and `arr_delay` from `flights`.

除了列出各个变量名外，给了另一个方法，其他就不管了。

```{r 5.4.1}
select(flights, starts_with("dep_"), starts_with("arr_"))
```

> 2.  What happens if you include the name of a variable multiple times in a select() call?

后续重复的变量会被忽略。一如文中使用`everything()`来调整顺序一样。

> 3.  What does the `any_of()` function do? Why might it be helpful in conjunction with this vector?
>
> ```{r, eval = FALSE}
> vars <- c("year", "month", "day", "dep_delay", "arr_delay")
> ```

会输出`vars`这个向量里面所有的变量。

> 4.  Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
>
> ```{r, eval = FALSE}
> select(flights, contains("TIME"))
> ```

它并不case sensitive！如果想要改变，加上`ignore.case = FALSE`。坦白说，很意外。不过，想来也是，如果总是case的，其实在筛选的时候反而增添了些麻烦。

## Exercise 5.5

> 1.  Currently `dep_time` and `sched_dep_time` are convenient to look at, but hard to compute with because they're not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r 5.5.1}
flights_new = mutate(
    flights,
    dep_time_new = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440,
    sched_dep_time_new = (sched_dep_time %/% 100 * 60 + sched_dep_time %%
                              100) %% 1440
)
```

> 2.  Compare `air_time` with `arr_time - dep_time`. What do you expect to see? What do you see? What do you need to do to fix it?

两个值肯定不相等。根据`flights`帮助页面，`air_time`是指飞行分钟数，而后者两个变量都是用HHMM形式表示的整数值，直接相见并不是时间差。所以，我们首先需要更改后者为分钟数再来比较：

```{r 5.5.2}
airtime <- transmute(flights,air_time,
    dep_time = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440,
    arr_time = (arr_time %/% 100 * 60 + arr_time %% 100) %% 1440,
    a2d = arr_time - dep_time,
    time_diff = air_time - a2d
  )
nrow(filter(airtime, time_diff != 0))
```

可是从结果来看，有327150行不相等。可能是因为记录的时间，跨过了午夜，因为数据里有负值；以及这些飞机的航线跨越了时区，按地方时记录的。虽然`airports`里记录了time zone信息，但我不确定用`tz`还是`tzone`，此处使用`tz`值。

因此做如下改动:

```{r 5.5.2b}
airtime <- flights  %>% left_join(select(nycflights13::airports, dest = faa, tz)) %>%  
  # 处理时区问题
  mutate(arr_time = arr_time - 100*(tz+5)) %>% filter(!is.na(arr_time)) %>%
  transmute(air_time,
    dep_time = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440,
    arr_time = (arr_time %/% 100 * 60 + arr_time %% 100) %% 1440,
    arr_time_new = ifelse(dep_time > arr_time, arr_time + 1440, arr_time), # 修正跨午夜问题
    a2d = arr_time_new - dep_time,
    time_diff = air_time - a2d
  )
nrow(filter(airtime, time_diff != 0))
airtime %>% ggplot(aes(time_diff))+geom_histogram()
```

虽然还是有差值，但基本上围绕在-235~49分钟之间。

> 3.  Compare `dep_time`, `sched_dep_time`, and `dep_delay`. How would you expect those three numbers to be related?

假设`dep_delay == dep_time - sched_dep_time`，然后我们可以如下检验：

```{r 5.5.3}
delaytime <- transmute(flights,dep_delay,
    dep_time = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440,
    sched_dep_time = (sched_dep_time %/% 100 * 60 + sched_dep_time %% 100) %% 1440,
    delay = dep_time - sched_dep_time,
    time_diff = (dep_delay - delay)
  )
nrow(filter(delaytime, time_diff != 0))
```

结果有1236个值不同，而且这个差值均为1440分钟。实际上是因为过了零点，而产生的计算上的差误。用上一题里使用的`ifelse`处理就好了。

> 4.  Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for `min_rank()`.

```{r 5.5.4}
delayed <- mutate(flights,
                  rank = min_rank(dep_delay))
arrange(delayed, rank)[1:10,]
```

> 5.  What does `1:3 + 1:10` return? Why?

我认为应该会报错，无法计算，但发现R会循环使用较短的向量来补齐。

> 6.  What trigonometric functions does R provide?

参见`?Trig`文档，主要的都有。

## Exercise 5.6

> 1.  Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:
>
> -   A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.
> -   A flight is always 10 minutes late.
> -   A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.
> -   99% of the time a flight is on time. 1% of the time it's 2 hours late. 
>
> Which is more important: arrival delay or departure delay?

直接回答最后的问题，迟到比迟发影响更大。延迟出发的话，可以在航线途中调整时间，但延迟到达的话，木已成舟。

> 2. Come up with another approach that will give you the same output as `not_cancelled %>% count(dest)` and `not_cancelled %>% count(tailnum, wt = distance)` (without using `count()`).

```{r 5.6.2}
# 根据书里，先构造not_cancelled数据集
not_cancelled <- flights %>% filter(!is.na(dep_delay), !is.na(arr_delay))
# 再来筛选计算
## same as `not_cancelled %>% count(dest)`
not_cancelled %>% group_by(dest) %>% summarise(n=n())
## same as `not_cancelled %>% count(tailnum, wt = distance)`
not_cancelled %>% group_by(tailnum) %>% summarise(total_distance = sum(distance))
```

除了上面的方法，也可以把`summarise()`改成`tally()`

> 3. Our definition of cancelled flights ( `is.na(dep_delay) | is.na(arr_delay)` ) is slightly suboptimal. Why? Which is the most important column?

```{r 5.6.3}
cancelled <- flights %>% filter(is.na(dep_delay) | is.na(arr_delay))
cancelled2 <- flights %>% filter(is.na(arr_delay))
identical(cancelled, cancelled2)
```

`dep_delay`这个条件是多余的。

> 4. Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?

只是每天的取消数量好像没有趋势。不过跟延迟的数量之间有较为密切的联系。

```{r 5.6.4}
cancelled_per_day <- flights %>% 
  mutate(cancelled = (is.na(arr_delay) | is.na(dep_delay))) %>% 
  group_by(year, month, day) %>% 
  summarise(cancelled_num = sum(cancelled), flights_num = n())

ggplot(cancelled_per_day) + geom_point(aes(x = cancelled_num, y = flights_num))

cancelled_delay <- flights %>% 
  mutate(cancelled = (is.na(arr_delay) | is.na(dep_delay))) %>% 
  group_by(year, month, day) %>% 
  summarise(
    cancelled_avg = mean(cancelled),
    dep_delay_avg = mean(dep_delay, na.rm = TRUE),
    arr_delay_avg = mean(arr_delay, na.rm = TRUE)
  )

ggplot(cancelled_delay, aes(x = dep_delay_avg, y = cancelled_avg)) + geom_point() + geom_smooth()
ggplot(cancelled_delay, aes(x = arr_delay_avg, y = cancelled_avg)) + geom_point() + geom_smooth()
```

> 5. Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about `flights %>% group_by(carrier, dest) %>% summarise(n())`)

第二个问题直接按照`arr_delay ~ carrier + dest + origin`做一个线性回归。

```{r 5.6.5}
# 按航线算的延误
carrier_delay <-
  flights %>% group_by(carrier) %>% summarise(
    arr_delay_avg = mean(arr_delay, na.rm = TRUE),
    dep_delay_avg = mean(dep_delay, na.rm = TRUE),
    delay_avg = (arr_delay_avg+dep_delay_avg) / 2
  ) %>% arrange(desc(delay_avg))

head(carrier_delay)
# 再看各机场的延误情况
dest_delay <-
  flights %>% group_by(dest) %>% summarise(arr_delay_avg = mean(arr_delay, na.rm = TRUE)) %>% arrange(desc(arr_delay_avg))
head(dest_delay)
```

> 6. What does the `sort` argument to `count()` do. When might you use it?

可以省一步使用arrange降序排列。

## Exercise 5.7

> 1. Refer back to the lists of useful mutate and filtering functions. Describe how each operation changes when you combine it with grouping.

此处需要注意的是数学计算函数不会受grouping影响，但统计量会被grouping影响。

> 2. Which plane (`tailnum`) has the worst on-time record?

首选筛除取消的航班，然后计算准点率，接着再筛除班次较少的（75%以下），最后再排序。

```{r 5.7.2}
flights %>% filter(!is.na(dep_delay), !is.na(arr_delay)) %>%
  mutate(on_time=arr_delay<=0) %>%
  group_by(tailnum) %>%
  summarise(on_time_rate=mean(on_time),flights_num=n()) %>%
  filter(flights_num>=110) %>%
  arrange(on_time_rate) %>%
  head()
```

> 3. What time of day should you fly if you want to avoid delays as much as possible?

早上飞，尽早飞。

```{r 5.7.3}
flights %>% filter(!is.na(arr_delay)) %>%
  group_by(hour) %>%
  summarise(delay_avg = mean(arr_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = hour, y = delay_avg)) + geom_point() + geom_smooth()
```

> 4. For each destination, compute the total minutes of delay. For each flight, compute the proportion of the total delay for its destination.

```{r 5.7.4}
flights %>% filter(arr_delay >= 0) %>% group_by(dest, flight) %>% summarise(total_min_flight = sum(arr_delay,na.rm = TRUE)) %>%
  mutate(
    total_min_dest = sum(total_min_flight),
    flight_prop = total_min_flight / total_min_dest
  )
```

> 5. Delays are typically temporally correlated: even once the problem that caused the initial delay has been resolved, later flights are delayed to allow earlier flights to leave. Using `lag()`, explore how the delay of a flight is related to the delay of the immediately preceding flight.

按照出发的机场、日期以及出发时间排序号之后，进行lag赋值；然后计算同样的延迟下，平均延误时间;最后看前一航班的延迟时长对后一航班平均延迟的影响。（其实用回归更清楚）

```{r 5.7.5}
flights %>% filter(!is.na(dep_time)) %>% arrange(origin, year, month, day, dep_time) %>%
  group_by(origin) %>% mutate(delay_lag=lag(dep_delay)) %>% filter(!is.na(delay_lag)) %>%
  group_by(delay_lag) %>% summarise(delay_mean=mean(dep_delay,na.rm=TRUE))%>%
  ggplot(aes(x=delay_lag,y=delay_mean))+geom_point()
```

> 6. Look at each destination. Can you find flights that are suspiciously fast? (i.e. flights that represent a potential data entry error). Compute the air time of a flight relative to the shortest flight to that destination. Which flights were most delayed in the air?

用箱线图里的离群值来判断是否可疑。

```{r 5.7.6}
flights %>% filter(!is.na(arr_time)) %>% group_by(dest) %>% 
  mutate(suspect = (air_time < (quantile(air_time, 1 / 4, na.rm = TRUE) - 1.5 * IQR(air_time, na.rm = TRUE))) |
    (air_time > (quantile(air_time, 3 / 4, na.rm = TRUE) + 1.5 * IQR(air_time, na.rm = TRUE)))) %>% ungroup() %>%
  filter(suspect)
```

> 7. Find all destinations that are flown by at least two carriers. Use that information to rank the carriers.

```{r 5.7.7}
flights %>% group_by(dest,carrier) %>% count(carrier) %>% filter(n>=2) %>% group_by(carrier) %>% count(sort = TRUE)
```

> 8. For each plane, count the number of flights before the first delay of greater than 1 hour.

```{r 5.7.8}
flights %>% select(tailnum, month, day, dep_time, arr_time, arr_delay) %>% filter(!is.na(arr_time)) %>% 
  arrange(tailnum, month, day, dep_time) %>% group_by(tailnum) %>%
  mutate(gt1h = cumsum(arr_delay > 60)) %>%
  summarise(num_flights = sum(gt1h < 1)) %>%
  arrange(desc(num_flights))
```

